---
title: "Kolada API Package With Shiny APP"
output:
  rmarkdown::html_document:
    code_folding: hide
    theme: lumen
vignette: >
  %\VignetteIndexEntry{Kolada API Package: Full Walkthrough}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

KoladaR is an R package that provides a convenient interface to the Kolada API, allowing users to explore Key Performance Indicators (KPIs) and Municipality data for Swedish regions directly from R.

The package also includes a Shiny application that provides an interactive GUI to browse, search, and filter Kolada KPIs and municipalities.

```{r, echo=FALSE, message=FALSE, warning=FALSE}
# Load required packages
library(openKolada)

cat("Check the Kolada API Base URL\n")
print(kolada_base())

cat("Load all the KPIs\n")
kpi <- get_kpi()
print(head(kpi))

cat("\nLoad KIPs for the specified KPI IDs\n")
kpi_selected <- get_kpi_by_Ids(c("N00011", "N00003"))
print(kpi_selected)

cat("Load all municipalities\n")
muni <- get_municipality()
print(head(muni))

cat("\nLoad municipalities for the specific municipalities IDs\n")
muni_selected <- get_municipality_by_Ids(c("0001", "0003"))
print(muni_selected)

```{r, echo=FALSE}
cat("Launch the interactive Shiny app by running the following command in your R console:\n\n")
cat("run_app()\n")



